\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant(TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Adrián Constante}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{senoreload.github.io}
% vs how you want it to show up. If it's you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://senoreload.github.io/}
\newcommand{\yourEmail}{ad\_con.reload@protonmail.ch}
\newcommand{\yourPhone}{+52 311 226 0149}
\newcommand{\githubUserName}{SenoReload}
\newcommand{\linkedInUserName}{aconstante}

 \alignProfileTable
 \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
     Email : \href{mailto:\yourEmail}{\yourEmail}
     \\
     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
     Mobile : \yourPhone
     \\
     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
     \\
 \end{tabular*}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{MSc. Computer Science}{Centro de Investigación y Estudios Avanzados del Instituto Politécnico Nacional}{Zapopan, Jalisco}{Sep 2019 - Sep 2021}

\courseWork{Software Engineering, Data Structures and Algorithms, Distributed Systems, Cryptography, Computer Networks, Machine Learning, High Performance Computing.}
\sectionsep

\educationHeading{BSc. Biomedical Engineering}{Universidad Politécnica de Sinaloa}{Mazatlán, Sinaloa}{Sep 2015 - Dec 2018}

\courseWork{Databases, OOP, Microcontrollers, Image \& Signal Processing, Analog \& Logic Desing, Metrology.}
\sectionsep

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}

\resumeHeading{HAVVOX IT AND DIGITAL INNOVATION}{D365 Software Dev Jr}{\\Mazatlán, Sinaloa}{March 2022 - March 2023}
\begin{bullets}
    \item I worked in technical consultory team on the development to deploy of a new product for the company Calidra, it is a Dynamics 365 Finance \& Operations project that will help to manage their clients and their projects sales.
    \item I pulled off many task involving classes, tables, forms, many other objects and its extensions and I also worked on the development of the frontend and documentation.
    \item Most of the task achieved required X++ on D365 Visual Studio Extension, in addition of cross-check validation and land Queries on SQL Server Managment Studio.
    \item As Microsoft partners we used Azure DevOps to manage the project, among other tools like Microsoft Teams for remote working, and we also used the agile methodology to manage the project.
\end{bullets}
\sectionsep

\resumeHeading{Conseil Européen pour la Recherche Nucléaire}{Research Assistant}{\\Meyrin, Switzerland}{Nov 2018 - Dec 2018}
\begin{bullets}
    \item Pure-teamwork between programmers, electronic engineers and physicists. to develop an enhancement for AD and V0 ALICE's detectors, the goal was to detect more particles.
    \item High-end oscilloscope measures were done to proof UAS proposed sensor could be used. We also developed a full report on the results and the project which was in count for the next cycles of upgrades of ALICE.
\end{bullets}
\sectionsep

\resumeHeading{Universidad Autónoma de Sinaloa}{Research Assistant}{\\Culiacán, Sinaloa}{Sep 2018 - Oct 2018}
\begin{bullets}
    \item An electronic SMD board with a 10-bits 1Gsps LVDS ADC was repaired with help of oscilloscope and review of the schematic and PCB desing.
    \item We developed the LVDS and HSMC protocol on FPGA to read data from the repaired board in order to make it work as planned. All of this on VHDL.
    \item This project was done in collaboration with the Physics Department of the UAS. It was prework for the next project which was to include the measurement module in ALICE at CERN.
\end{bullets}
\sectionsep

\resumeHeading{CINVESTAV del Instituto Politecnico Nacional}{Research Assistant}{\\Zapopan, Jalisco}{Nov 2017 - Dec 2017}
\begin{bullets}
    \item Robotic related calculations and desing were made to achieve the goal, we did a full review on math involved as we worked on Control Theory area.
    \item We developed the control for a haptic robot arm to help kids with rehabilitation of their entire superior members using MatLab.
\end{bullets}
\sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Major Projects}

\projectHeading{Electronic Health Record System(2020)}{https://github.com/alison82/MedicalHistory-BlockChainProject}{Blockchain, Solidity, IPFS}
\begin{bullets}
    \item Teamwork activities to develop a database about EHR, ensuring the fidelity and secrecy of patient data. My main task was to develope a requirement about an access control on who can CRUD patient and medical workers data.
    \item The Etherum Smart Contracts needed were developed with Truffle framework, once ready deployment was done on Kovan Etherum testnet and IPFS.
\end{bullets}

\sectionsep

\projectHeading{Facial Gesture-driven Wheel Chair(2018)}{https://github.com/SenoReload/deep-chair}{OpenCV, CNN, Python, Arduino}
\begin{bullets}
    \item A special electric wheelchair was developed for quadriplegic people using computer vision and deep learning (CNN). It was able to move with facial gestures like moving head in some directions.
    \item We developed the entire dataset with face images plus data augmentation. We used and trained a PyTorch image classifier, ResNet18, then we developed the electronics needed.
\end{bullets}
\sectionsep

\projectHeading{SeaHawk: Security for Mazatlan’s beaches(2018)}{https://github.com/SenoReload}{OpenCV, CNN, AWS, Python}

\begin{bullets}
    \item It was a computer vision system able to recognize if people were too off the coast. Main idea was to help lifeguards in Mazatlan Beaches so
    we used a Mask-RCNN implemented on TensorFlow. 
    \item We used a Raspberry Pi 3B+ with a camera module to capture images, then we used OpenCV to post-process images in the sake of make them fittable for CNN model.
    \item We segmented the video between beach, sea, and people, then train the model on AWS instance. We won a hackathon with it.
\end{bullets}
\sectionsep  

\projectHeading{A Haptic Robot Arm(2017)}{https://github.com/SenoReload}{Robotics, Control Theory, MatLab, Arduino}
\begin{bullets}
    \item We developed a planar haptic robot arm to help kids with rehabilitation of their entire superior members. The robot was designed and manufactered with help of SolidWorks.
    \item We coded routines like circle movements to help them to improve, then retrieve data to measure how their improvement was. PID control and robotics calculations were implemented on MATLAB and Arduino.
\end{bullets}
\sectionsep  
%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \doubleItem{Languages:}{C/C++, Python, SQL}
               {Databases:}{\href{https://www.microsoft.com/en-us/sql-server/}{SQL Server}, \href{https://tinydb.readthedocs.io/en/latest/}{TinyDB}}
    \\
    \doubleItem{Web Development:}{Django}
               {Technology:}{Git, \LaTeX}
    \\
    \doubleItem{Online Curses:}{\href{https://www.udemy.com/certificate/UC-NTRR1TAC/}{Python}}
               {Frameworks:}{\href{https://www.trufflesuite.com/}{Truffle}}
   \\
    \doubleItem{Hardware:}{Arduino, Raspberry Pi \& Pico W}
               {Other:}{PC Hardwre, Laser Cutting, Azure DevOps}
    
    \end{skillList}
\end{document}